Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-31 VMCAI-revised-version/final.tex
up

We now consider the case $\Safe = \mathop{\downarrow} \Safe$.
%
Unfortunately {\sc State-resilience} is undecidable in this case. As for {\sc Resilience} in WSTS when $\Safe = \mathop{\downarrow} \Safe$, this stems from undeciability of the 
{\sc Structural existential halting} of reset-VASS.
%\mathieu{GOTO}

@@

Now, executions of Minsky machines can be simulated by reset-VASS~\cite{araki1976PN,dufourd1998reset}. 
% \alain{\cite{araki1976PN} simule-t-il les Minsky machines et comment ?}
%Reset-VASS extend the basic VASS model with special “reset
%transitions” that set to $0$ some coordinates in the vector. 
%			Let us recall their definition here.
%      	it is well known that reset-VASS are WSTS~\cite{dufourd1998reset}.
The simulation operates by building a reset-VASS 
which mimick the behaviors of the Minsky machines' counters by using two mirror counters 
for each of them,
and in which
there exists
 a sequence from 
an initial state %$(s,x_1 \ldots x_n)$
	with equal mirror counters
to
a state $ q({\bf 0})$ if and only if
there exists
a sequence
 in the Minsky machine
 from a corresponding initial state
 to
 the state $q_f(0,0,0)$
  (from Theorem~$5$ in \cite{araki1976PN}).
  []
Hence {\sc Resilience} (resp. {\sc State resilience}) holds in the Minsky machine $M'$ iff 
{\sc Resilience} (resp. {\sc State resilience}) holds in the reset-VASS simulating $M'$.
Since reset-VASS can simulate executions of a Minsky machine, {\sc Resilience} 
and  {\sc State-resilience} are undecidable for reset-VASS and hence for  $\pred$-basis-effective, 
$\omega^2$-WSTS with strong compatibility as well.\qed
\end{proof}

>>>>

We now consider the case $\Safe = \mathop{\downarrow} \Safe$.
%
Unfortunately {\sc State-resilience} is undecidable in this case. 
%\mathieu{GOTO}
Unfortunately {\sc State-resilience} is undecidable in this case. As for {\sc Resilience} in WSTS when $\Safe = \downarrow \Safe$, this stems from undeciability of the corresponding problem in Minsky machines, the executions of which can be simulated by reset-VASS, as seen in 
Section~\ref{safe-down} and devellopped more in Appendix~\ref{minsk}.

@@

Now, executions of Minsky machines can be simulated by reset-VASS~\cite{araki1976PN,dufourd1998reset}. 
% \alain{\cite{araki1976PN} simule-t-il les Minsky machines et comment ?}
%Reset-VASS extend the basic VASS model with special “reset
%transitions” that set to $0$ some coordinates in the vector. 
%			Let us recall their definition here.
%      	it is well known that reset-VASS are WSTS~\cite{dufourd1998reset}.
The simulation operates by building a reset-VASS 
which mimick the behaviors of the Minsky machines' counters by using two mirror counters 
for each of them,
and in which
there exists
 a sequence from 
an initial state %$(s,x_1 \ldots x_n)$
	with equal mirror counters
to
a state $ q({\bf 0})$ if and only if
there exists
a sequence
 in the Minsky machine
 from a corresponding initial state
 to
 the state $q_f(0,0,0)$
  (from Theorem~$5$ in \cite{araki1976PN}).
  [... from initial states with unequal mirror counters ... -> go back to a state with equal mirror counters -> then ...]
Hence {\sc Resilience} (resp. {\sc State resilience}) holds in the Minsky machine $M'$ iff 
{\sc Resilience} (resp. {\sc State resilience}) holds in the reset-VASS simulating $M'$.
Since reset-VASS can simulate executions of a Minsky machine, {\sc Resilience} 
and  {\sc State-resilience} are undecidable for reset-VASS and hence for  $\pred$-basis-effective, 
$\omega^2$-WSTS with strong compatibility as well.\qed
\end{proof}
